\section{Documentation}
Once the provider has been added to the Terraform Registry, the documentation will be available online there.
For the purpose of this workshop, the documentation is being temporarily hosted on \href{https://intuinewin.github.io/taikun-docs/}{Github Pages}.

\section{Tasks}
The ultimate goal of this workshop is to have an operational Taikun project built solely with Terraform
configuration files.
By following a step by step process, you will discover how various Taikun
resources are declared and managed using Terraform.\\

All your work will be done in the \texttt{workshop/} directory.
\begin{raw}
./workshop/
|-- main.tf
|-- taikun_auth.auto.tfvars
|-- variables.tf
\end{raw}
\texttt{main.tf} contains the Provider configuration, namely where it is installed
and what credentials to use. You will not need to edit this file.
\begin{tf}
# main.tf
terraform {
  required_providers {
    taikun = {
      source = "itera-io/dev/taikun"
    }
  }
}

provider "taikun" {
  email    = var.taikun_email
  password = var.taikun_password
}
\end{tf}
In fact, Terraform reads its configuration from all the files with the extension \texttt{.tf},
in the working directory. The extension \texttt{.tfvars} will be discussed later.
Having the provider configuration in \texttt{main.tf} is simply a convention.
During this workshop, each task should be coded in a separate config file,
such that, at the end of the workshop, your directory is organized as such:
\begin{raw}
./workshop/
|-- main.tf
|-- taikun_auth.auto.tfvars
|-- task0.tf
|-- task1.tf
|-- task2.tf
|-- task3.auto.tfvars
|-- task3.tf
|-- task4.tf
|-- task5.tf
|-- variables.tf
|-- users.auto.tfvars
|-- users.tf
\end{raw}
% TODO update as tasks are added

\begin{warn}
  Throughout this workshop, in order to avoid conflicts and
  to permit easy clean up of leftover infrastructure, please follow the naming conventions used below.\\

  All resources names will follow the format \texttt{tfws-<firstname>-<s>}, where:
  \begin{itemize}
    \item \texttt{<firstname>} is your firstname
    \item \texttt{<s>} is an arbitrary string of your choosing
  \end{itemize}
  For example, Jane Doe might name their Taikun project \texttt{tfws-jane-mysuperproject}.
\end{warn}

\subsection{Authentication}\label{sec:auth}
In order to complete the tasks that follow, you will need to provide Taikun credentials to Terraform.
You will be using a Partner account, as some of the tasks, such as creating an organization,
require Partner privileges.\\

We will explain how input variables work later in the workshop.
For now, simply edit \texttt{taikun\_auth.auto.tfvars}
and replace the values of \texttt{taikun\_email} and \texttt{taikun\_password}
with the credentials provided on the \textbf{\#terraform-workshop} Slack channel.
\begin{tf}
# taikun_auth.auto.tfvars
taikun_email = "jane.doe@itera.io"
taikun_password = "PassWord123"
\end{tf}
To find out more about providing sensitive data to Terraform, see this \href{https://learn.hashicorp.com/tutorials/terraform/sensitive-variables}{Hashicorp tutorial}.

\input{task0}
\input{task1}
\input{task2}
\input{task3}
\input{task4}
\input{task5}
